\vspace{-1in} Demystifying the Computer Science \\PhD Admission in US Universities\\{\large A guide for Vietnamese and International Students

### 2023-07-05 phd-cs-us.tex
updates

If you want to contact a prof. to ask about \emph{research opportunities}, or \emph{GTA/GRA} support, then \emph{yes}, I believe you should, but you really have to write your mail in a certain way. 
First, read the prof's website, see if they are saying something about contacting them. Many profs. indicate what you should do to contact them (e.g., specific email subjects). 
In general, the best way to catch the prof.'s attention is to \emph{customize your email} to that specific faculty.  For example, read their papers, know what they work on, and see if you are interested in their research.  If you are, then you can send them an email talking how/why their work would match yours.
In contrast, if you write a generic email that can be sent to multiple professors (e.g., if you just change some names and keywords in the email), you will not get any response.

@@

I read your TSE paper on numerical invariant generation, and I am interested in this line of dynamic invariant research. I have worked (optional: with prof. Y at Z) on static analysis on C programs and I think it would be a good fit to tackle the spurious issues mentioned in your paper. I have a small paper at conference/workshop C and a project on symbolic execution at Github G.

>>>>

If you want to contact a prof. to ask about \emph{research opportunities}, or \emph{GTA/GRA} support, then \emph{yes}, I believe you should---it is \emph{worth it}. 
First, read the prof's website, see if they say something about contacting them. Many profs. indicate how prospective students should contact them (e.g., specific email subjects). 
In general, the best way to catch the prof.'s attention is to \emph{customize your email} to that faculty.  For example, read their papers, know what they work on, and see if you are interested in their research. Then send them an email talking how/why their work would match yours.
In contrast, if you write a generic email that can be sent to multiple professors (e.g., if you just change some names and keywords in the email), you will not likely get a response.

@@

I read your TSE'21 paper on numerical invariant generation, and I am interested in this line of dynamic invariant research. I have worked (optional: with prof. Y at Z) on static program analysis and I think it could be used to tackle the spurious issues mentioned in your paper. I have a small paper at conference/workshop C and a project on symbolic execution at Github G.
